Structuring College Access: The Market Segment Model and College Board Geomarkets

### 2025-04-30 text/back_end_KS.qmd
smoothing LA rq2

### Composition of Students Lists by Geomarkets \[Need Better RQ2 Heading\]

@@

>>>>

@@

Despite Los Angeles's multi-nuclei urban structure contributing to a more decentralized Geomarket landscape with racial/ethnic diversity across a range of socioeconomic levels more spatially distributed across the metropolitan area, Geomarkets contributions to student prospect pools reflect racial and socioeconomic stratification patterns similar to other metropolitan cases in the study. Affluent Geomarkets like San Fernando Valley–West and West Los Angeles contribute an overrepresentation of White, Asian, and not-first generation college student prospects, the magnitude of which increases substantially as score ranges increase (see Appendix @fig-la-rq2-lowSAT-race and @fig-la-rq2-highSAT-race). On the other hand, more diverse and historically low-income Geomarkets, like South and South Central Los Angeles and Riverside, San Bernardino, and Ontario, contribute disproportionately more Black, Hispanic, and first-generation college student prospects. Similar to Chicago and Dallas-Fort Worth, Los Angeles further solidifies the pattern of some of the lowest-income Geomarkets consistently playing crucial roles in fostering college access for first-generation Asian (East Los Angeles), Black (South and South Central Los Angeles), and Hispanic college students (South and South Central Los Angeles, East Los Angeles, Hollywood and Wilshire, and Riverside, San Berdardino, and Ontario).
